---
title: "Visualization Project on LUNG CANCER"
author: "REEWA MALIK-MDS202134"
date: "30/11/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#The data used for the project is a survey data, which has variables #"GENDER","AGE","SMOKING","YELLOW_FINGERS","ANXIETY"               #"PEER_PRESSURE","CHRONIC.DISEASE","FATIGUE","ALLERGY"               #"WHEEZING","ALCOHOL.CONSUMING","COUGHING",
#"SHORTNESS.OF.BREATH","SWALLOWING.DIFFICULTY","CHEST.PAIN","LUNG_CANCER#".The idea is to study the relationship between LUNG_CANCER and other #variables, which are as follows-

#1.What is the percentage of people who didn't smoke(and other varaibles #too) but still has lung Cancer and what is the percentage of people who #smoke but still didnt get lung cancer?

#2.Is it common for a certain age group to have lung cancer?
#3.What are the major factors that causes lung cancer and what are not?
#4.Can the results obtained from the given data be generalised.
#5.Do people in the dataset lead a healthy lifestyle?

```{r}
library('ggplot2')
lung_cancer_data=read.csv(file.choose())
```

```{r}
names(lung_cancer_data)

```
#For the Project, I am considering variables  "AGE",                  #"SMOKING","ANXIETY", "CHRONIC.DISEASE" ,"ALCOHOL.CONSUMING" #,"COUGHING","SHORTNESS.OF.BREATH" ,"CHEST.PAIN","LUNG_CANCER".

# Out of these variables, the variable AGE is a continuous random #variable and rest are all categorical and to be specific all are #Nominal, since they do not have any intrinsic order,its just Yes or No. #For some of these variables, 1 represents NO and 2 represents YES.

```{r}
tab <- matrix(rep('Nominal', times=9), ncol=9, byrow=TRUE)
colnames(tab) <- c('AGE', 'SMOKING', 'ANXIETY', 'CHRONIC.DISEASE','ALCOHOL.CONSUMING','COUGHING','SHORTNESS.OF.BREATH',
    'CHEST.PAIN','LUNG_CANCER')
rownames(tab) <- c('TYpe of Variable')
tab[1,1]='Continuous'
tab
#The given table represents which considered variable is Continuous and #which is Nominal(Categorical)
```
#UNIVARIATE ANALYSIS OF DIFFERENT VARIABLES
```{r}
#Making the histogram to check,data set has which age group in most #numbers.
hist(lung_cancer_data$AGE, col = 'pink', breaks = seq(min(lung_cancer_data$AGE), max(lung_cancer_data$AGE), length.out = 15))
table(lung_cancer_data$AGE)
summary(lung_cancer_data$AGE)

#Clearly the data has majority of the people IN age group 54-72.So #whatever results we get from this data set cannot be generalised for #every age group.
```



```{r}
table(lung_cancer_data$SMOKING)#No of people who smoke and who don't
ggplot(lung_cancer_data, 
       aes(x = SMOKING, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "SMOKING", 
       y = "Percent", 
       title  = "SMOKING PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "coral")
#Approx 57 percent people smoke and approx 43 percent people don't.
```


```{r}
table(lung_cancer_data$ANXIETY)#No of people who have anxiety and who don't
ggplot(lung_cancer_data, 
       aes(x = ANXIETY, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "ANXIETY", 
       y = "Percent", 
       title  = "ANXIETY PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "lightgreen")
#Approx 50 percent people have anxiety and approx 50 percent people #don't.
```


```{r}
table(lung_cancer_data$CHRONIC.DISEASE)#No of people who have chronic #disease and who don't
ggplot(lung_cancer_data, 
       aes(x = CHRONIC.DISEASE, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "CHRONIC.DISEASE", 
       y = "Percent", 
       title  = "CHRONIC.DISEASE PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "blue")
#Approx 51 percent people have chronic disease and approx 49 percent #people don't.
```
```{r}
table(lung_cancer_data$ALCOHOL.CONSUMING)#No of people who consume #alcohol and who don't
ggplot(lung_cancer_data, 
       aes(x = ALCOHOL.CONSUMING, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "ALCOHOL.CONSUMING", 
       y = "Percent", 
       title  = "ALCOHOL.CONSUMING PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "lightpink")
#Approx 57 percent consume alcohol and 43 percent don't consume alcohol.
```
```{r}
table(lung_cancer_data$COUGHING)#No of people who have cough and who #don't
ggplot(lung_cancer_data, 
       aes(x = COUGHING, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "COUGHING", 
       y = "Percent", 
       title  = "COUGHING PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "red")
#Approx 58 percent have cough and 42 percent don't have cough.
```
```{r}
table(lung_cancer_data$SHORTNESS.OF.BREATH)#No of people who have #shortness of breath and who don't
ggplot(lung_cancer_data, 
       aes(x = SHORTNESS.OF.BREATH, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "SHORTNESS.OF.BREATH", 
       y = "Percent", 
       title  = "SHORTNESS.OF.BREATH PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "yellow")
#Approx 64 percent have SHORTNESS.OF.BREATH and 36 percent don't have #SHORTNESS.OF.BREATH.
```
```{r}
table(lung_cancer_data$CHEST.PAIN)#No of people who have chest pain and #who don't
ggplot(lung_cancer_data, 
       aes(x = CHEST.PAIN, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "CHEST.PAIN", 
       y = "Percent", 
       title  = "CHEST.PAIN PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "#66CDAA")
#Approx 56 percent have CHEST.PAIN and 44 percent don't have CHEST.PAIN.

```
```{r}
table(lung_cancer_data$LUNG_CANCER)#No of people who have lung cancer #and who don't
ggplot(lung_cancer_data, 
       aes(x = LUNG_CANCER, 
           y = ..count.. / sum(..count..))) + 
  geom_bar() +
  labs(x = "LUNG_CANCER", 
       y = "Percent", 
       title  = "LUNG_CANCER PERCENTAGE") +
  scale_y_continuous(labels = scales::percent)+geom_bar(fill = "#FFBBFF")
#Approx 87.5 percent have LUNG_CANCER and 12.5 percent don't have #LUNG_CANCER.
```

#BIVARIATE ANALYSIS 
```{r}
my_tab<-table(lung_cancer_data$SMOKING,lung_cancer_data$LUNG_CANCER)
my_tab#No of people who have Lung Cancer and who Smoke 
#1-NO,2-YES for SMOKING
```
```{r}
my_tab<-table(lung_cancer_data$ANXIETY,lung_cancer_data$LUNG_CANCER)
my_tab#No of people who have Lung Cancer and who have Anxiety
#1-NO,2-YES for ANXIETY
```
```{r}
my_tab<-table(lung_cancer_data$CHEST.PAIN,lung_cancer_data$LUNG_CANCER)
my_tab#No of people who have Lung Cancer and who have chest pain
#1-NO,2-YES for CHEST.PAIN
```
```{r}
my_tab<-table(lung_cancer_data$ALCOHOL.CONSUMING,lung_cancer_data$LUNG_CANCER)
my_tab#No of people who have Lung Cancer and who consume alcohol
#1-NO,2-YES for ALCOHOL.CONSUMING
```

```{r}
my_tab<-table(lung_cancer_data$SHORTNESS.OF.BREATH,lung_cancer_data$LUNG_CANCER)
my_tab#No of people who have Lung Cancer and who have SHORTNESS.OF.BREATH
#1-NO,2-YES for SHORTNESS.OF.BREATH
```
```{r}
my_tab<-table(lung_cancer_data$COUGHING,lung_cancer_data$LUNG_CANCER)
my_tab#No of people who have Lung Cancer and who have COUGHING
#1-NO,2-YES for COUGHING
```
```{r}
my_tab<-table(lung_cancer_data$CHRONIC.DISEASE,lung_cancer_data$LUNG_CANCER)
my_tab#No of people who have Lung Cancer and who have CHRONIC.DISEASE
#1-NO,2-YES for CHRONIC.DISEASE
```
```{r}

library(ggplot2)
```
```{r}
library(dplyr)
```

```{r}
#Lets find out what percentage of people have lung cancer and also a  #YES for considered Categorical variables.
a=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',SMOKING==2))
b=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',ANXIETY==2))
c=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',CHEST.PAIN==2))
d=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',COUGHING==2))
e=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',ALCOHOL.CONSUMING==2))
f=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES', CHRONIC.DISEASE==2))
g=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',SHORTNESS.OF.BREATH==2))
n=nrow(lung_cancer_data)
smoking_positive_cancer_positive_percentage=(a/n)*100
smoking_positive_cancer_positive_percentage#Approx 50% people who smoke #have Lung Cancer.
anxiety_positive_cancer_positive_percentage=(b/n)*100
anxiety_positive_cancer_positive_percentage#Approx 46% people who suffer #from Anxiety have Lung Cancer
chest.pain_positive_cancer_positive_percentage=(c/n)*100
chest.pain_positive_cancer_positive_percentage#Approx 52% people who #suffer from Chest Pain have Lung Cancer
coughing_positive_cancer_positive_percentage=(d/n)*100
coughing_positive_cancer_positive_percentage#Approx 55% people who #suffer from Coughing problem have Lung Cancer
ALCOHOL.CONSUMING_cancer_positive_positive_percentage=(e/n)*100
ALCOHOL.CONSUMING_cancer_positive_positive_percentage#Approx 53% people #who consume Alcohol  have Lung Cancer
CHRONIC.DISEASE_cancer_positive_positive_percentage=(f/n)*100
CHRONIC.DISEASE_cancer_positive_positive_percentage#Approx 46% people #who suffer from some Chronic disease have Lung Cancer
SHORTNESS.OF.BREATH_cancer_positive_positive_percentage=(g/n)*100
SHORTNESS.OF.BREATH_cancer_positive_positive_percentage#Approx 57% #people who suffer from Shortness of Breathness problem have Lung Cancer

```

```{r}
#Lets find out what percentage of people don't have lung cancer and also #a  YES for one of the considered Categorical variables.
a=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',SMOKING==2))
b=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',ANXIETY==2))
c=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',CHEST.PAIN==2))
d=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',COUGHING==2))
e=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',ALCOHOL.CONSUMING==2))
f=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO', CHRONIC.DISEASE==2))
g=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',SHORTNESS.OF.BREATH==2))
n=nrow(lung_cancer_data)
smoking_positive_cancer_negative_percentage=(a/n)*100
smoking_positive_cancer_negative_percentage#Approx 6% people  smoke but #do not have Lung Cancer.
anxiety_positive_cancer_negative_percentage=(b/n)*100
anxiety_positive_cancer_negative_percentage#Approx 4% people have #anxiety issues but do not have Lung Cancer.
chest.pain_positive_cancer_negative_percentage=(c/n)*100
chest.pain_positive_cancer_negative_percentage#Approx 4% people have #Chest pain but do not have Lung Cancer.
coughing_positive_cancer_negative_percentage=(d/n)*100
coughing_positive_cancer_negative_percentage#Approx 3% people have #coughing problem but do not have Lung Cancer.
ALCOHOL.CONSUMING_positive_cancer_negative_percentage=(e/n)*100
ALCOHOL.CONSUMING_positive_cancer_negative_percentage#Approx 2% people #smoke but do not have Lung Cancer.
CHRONIC.DISEASE_positive_cancer_negative_percentage=(f/n)*100
CHRONIC.DISEASE_positive_cancer_negative_percentage#Approx 5% people #have Chronic disease but do not have Lung Cancer.
SHORTNESS.OF.BREATH_positive_cancer_negative_percentage=(g/n)*100
SHORTNESS.OF.BREATH_positive_cancer_negative_percentage#Approx 7% people #have shortness of breath problem but do not have Lung Cancer.

#As indicated by all the precentages, it is quite a rare chance that any #person who smoke,has anxiety issues,chest pain,cough,chronic #disease,shortness of breath and consume alcohol will not have lung #cancer. So we can imply from here, its better to avoid whatever we can #from all of the above variables.

```

```{r}
#Lets find out what percentage of people don't have lung cancer and also #a NO for one of the considered Categorical variables.
a=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',SMOKING==1))
b=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',ANXIETY==1))
c=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',CHEST.PAIN==1))
d=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',COUGHING==1))
e=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',ALCOHOL.CONSUMING==1))
f=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO', CHRONIC.DISEASE==1))
g=nrow(filter(lung_cancer_data, LUNG_CANCER == 'NO',SHORTNESS.OF.BREATH==1))
n=nrow(lung_cancer_data)
smoking_negative_cancer_negative_percentage=(a/n)*100
smoking_negative_cancer_negative_percentage#There are Approx 6% people  #who don't smoke and do not have Lung Cancer.
anxiety_negative_cancer_negative_percentage=(b/n)*100
anxiety_negative_cancer_negative_percentage#There are Approx 9% people  #who don't have anxiety and do not have Lung Cancer.
chest.pain_negative_cancer_negative_percentage=(c/n)*100
chest.pain_negative_cancer_negative_percentage#There are Approx 9% #people  who don't have chest pain and do not have Lung Cancer.
coughing_negative_cancer_negative_percentage=(d/n)*100
coughing_positive_cancer_negative_percentage#There are Approx 3% people #who don't have coughing problem and do not have Lung Cancer.
ALCOHOL.CONSUMING_negative_cancer_negative_percentage=(e/n)*100
ALCOHOL.CONSUMING_negative_cancer_negative_percentage#There are Approx #10% people  who don't consume and do not have Lung Cancer.
CHRONIC.DISEASE_negative_cancer_negative_percentage=(f/n)*100
CHRONIC.DISEASE_negative_cancer_negative_percentage#There are Approx 8% #people  who don't have chronic disease and do not have Lung Cancer.
SHORTNESS.OF.BREATH_negative_cancer_negative_percentage=(g/n)*100
SHORTNESS.OF.BREATH_negative_cancer_negative_percentage#There are Approx #5% people  who don't have shortness of breath and do not have Lung #Cancer.
#As indicated by all the precentages, it is quite a rare chance that any #person who don't smoke,do not have anxiety issues,chest #pain,cough,chronic disease,shortness of breath and don't consume #alcohol will not have lung cancer. So we can imply from here that even #if someones avoids all the above variables,still there is a very less #chance that the person will not suffer from Lung Cancer. So may be #there are some other factors other than these which cause lung Cancer.
```
```{r}
#Lets find out what percentage of people have lung cancer and also a NO #for one of the Categorical variable.
a=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',SMOKING==1))
b=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',ANXIETY==1))
c=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',CHEST.PAIN==1))
d=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',COUGHING==1))
e=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',ALCOHOL.CONSUMING==1))
f=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES', CHRONIC.DISEASE==1))
g=nrow(filter(lung_cancer_data, LUNG_CANCER == 'YES',SHORTNESS.OF.BREATH==1))
n=nrow(lung_cancer_data)
smoking_negative_cancer_positive_percentage=(a/n)*100
smoking_negative_cancer_positive_percentage#There are Approx 37% people #who don't smoke and have Lung Cancer.
anxiety_negative_cancer_positive_percentage=(b/n)*100
anxiety_negative_cancer_positive_percentage#There are Approx 41% people #who don't have anxiety and have Lung Cancer.
chest.pain_negative_cancer_positive_percentage=(c/n)*100
chest.pain_negative_cancer_positive_percentage#There are Approx 36% #people  who don't have chest pain and have Lung Cancer.
coughing_negative_cancer_positive_percentage=(d/n)*100
coughing_negative_cancer_positive_percentage#There are Approx 33% 
#people who don't have coughing problem and have Lung Cancer
ALCOHOL.CONSUMING_negative_cancer_positive_percentage=(e/n)*100
ALCOHOL.CONSUMING_negative_cancer_positive_percentage#There are Approx #34% people  who don't consume alcohol and have Lung Cancer.
CHRONIC.DISEASE_negative_cancer_positive_percentage=(f/n)*100
CHRONIC.DISEASE_negative_cancer_positive_percentage#There are Approx 41% #people  who don't have chronic disease and do not have Lung Cancer
SHORTNESS.OF.BREATH_negative_cancer_positive_percentage=(g/n)*100
SHORTNESS.OF.BREATH_negative_cancer_positive_percentage#There are Approx #30% people  who don't have shortness of breath and have Lung Cancer.
#As indicated by all the precentages, there is high chance that any #person who don't smoke,do not have anxiety issues,chest #pain,cough,chronic disease,shortness of breath and don't consume #alcohol will still have lung cancer. So we can imply from here that #even if someones avoids all the above variables,still there is a high #chance that the person will suffer from Lung Cancer. So may be there #are some other factors other than these which cause lung Cancer.

```


```{r}
library('ggplot2')
ggplot(lung_cancer_data, aes(x =SMOKING, fill =LUNG_CANCER )) + 
  geom_bar(position = "stack")
#Bar plot representing no of people who have cancer and who don't out 
#of those who smoke and don't smoke.
```
```{r}
ggplot(lung_cancer_data, 
       aes(x =ANXIETY, 
           fill =LUNG_CANCER )) + 
  geom_bar(position = "stack")
#Bar plot representing no of people who have cancer and who don't out 
#of those who have anxiety and  who don't have anxiety.
```
```{r}
ggplot(lung_cancer_data, 
       aes(x =COUGHING, 
           fill =LUNG_CANCER )) + 
  geom_bar(position = "stack")
#Bar plot representing no of people who have cancer and who don't out 
#of those who have cough and don't.
```

```{r}
ggplot(lung_cancer_data, 
       aes(x =CHRONIC.DISEASE, 
           fill =LUNG_CANCER )) + 
  geom_bar(position = "stack")
#Bar plot representing no of people who have cancer and who don't out 
#of those who have chronic disease and who don't.
```
```{r}
ggplot(lung_cancer_data, 
       aes(x =ALCOHOL.CONSUMING, 
           fill =LUNG_CANCER )) + 
  geom_bar(position = "stack")
#Bar plot representing no of people who have cancer and who don't out 
#of those who consume alcohol and who don't.
```
```{r}
ggplot(lung_cancer_data, 
       aes(x =SHORTNESS.OF.BREATH, 
           fill =LUNG_CANCER )) + 
  geom_bar(position = "stack")
#Bar plot representing no of people who have cancer and who don't out 
#of those who have shortness of breath and who don't.
```
```{r}
ggplot(lung_cancer_data, 
       aes(x =CHEST.PAIN, 
           fill =LUNG_CANCER )) + 
  geom_bar(position = "stack")
#Bar plot representing no of people who have cancer and who don't out 
#of those who have chest pain and who don't.
```

```{r}
lung_cancer_data_con <- within(lung_cancer_data, {  
  SMOKING.Con<-NA
  SMOKING.Con[SMOKING==1] <- "NO"
  SMOKING.Con[SMOKING==2] <- "YES"

   })
ggplot(lung_cancer_data_con, 
       aes(x =AGE, 
           fill =SMOKING.Con )) + 
  geom_bar(position = "stack")
#bar plot representing people of particular age smoking and not smoking.
```
```{r}
lung_cancer_data_con1 <- within(lung_cancer_data, {  
  ANXIETY.Con<-NA
  ANXIETY.Con[ANXIETY==1] <- "NO"
 ANXIETY.Con[ANXIETY==2] <- "YES"

   })
ggplot(lung_cancer_data_con1, 
       aes(x =AGE, 
           fill =ANXIETY.Con )) + 
  geom_bar(position = "stack")
#bar plot representing people of particular age having anxiety or not.
```
```{r}
lung_cancer_data_con2 <- within(lung_cancer_data, {  
  ALCOHOL.CONSUMING.Con<-NA
  ALCOHOL.CONSUMING.Con[ALCOHOL.CONSUMING==1] <- "NO"
 ALCOHOL.CONSUMING.Con[ALCOHOL.CONSUMING==2] <- "YES"

   })
ggplot(lung_cancer_data_con2, 
       aes(x =AGE, 
           fill =ALCOHOL.CONSUMING.Con )) + 
  geom_bar(position = "stack")
#bar plot representing people of particular age consuming alcohol or #not.
```
```{r}
lung_cancer_data_con3 <- within(lung_cancer_data, {  
  CHRONIC.DISEASE.Con<-NA
  CHRONIC.DISEASE.Con[CHRONIC.DISEASE==1] <- "NO"
CHRONIC.DISEASE.Con[CHRONIC.DISEASE==2] <- "YES"

   })
ggplot(lung_cancer_data_con3, 
       aes(x =AGE, 
           fill =CHRONIC.DISEASE.Con )) + 
  geom_bar(position = "stack")
#bar plot representing people of particular age having chronic disease #or not.
```
```{r}
lung_cancer_data_con4 <- within(lung_cancer_data, {  
  COUGHING.Con<-NA
  COUGHING.Con[COUGHING==1] <- "NO"
COUGHING.Con[COUGHING==2] <- "YES"

   })
ggplot(lung_cancer_data_con4, 
       aes(x =AGE, 
           fill =COUGHING.Con )) + 
  geom_bar(position = "stack")
#bar plot representing people of particular age having cough or 
#not.
```
```{r}
lung_cancer_data_con5 <- within(lung_cancer_data, {  
  CHEST.PAIN.Con<-NA
  CHEST.PAIN.Con[CHEST.PAIN==1] <- "NO"
 CHEST.PAIN.Con[CHEST.PAIN==2] <- "YES"

   })
ggplot(lung_cancer_data_con5, 
       aes(x =AGE, 
           fill =CHEST.PAIN.Con )) + 
  geom_bar(position = "stack")
#bar plot representing people of particular age having chest pain or #not.
```
```{r}
lung_cancer_data_con6 <- within(lung_cancer_data, {  
  SHORTNESS.OF.BREATH.Con<-NA
  SHORTNESS.OF.BREATH.Con[SHORTNESS.OF.BREATH==1] <- "NO"
 SHORTNESS.OF.BREATH.Con[SHORTNESS.OF.BREATH==2] <- "YES"

   })
ggplot(lung_cancer_data_con6, 
       aes(x =AGE, 
           fill =SHORTNESS.OF.BREATH.Con )) + 
  geom_bar(position = "stack")
#bar plot representing people of particular age having shortness of #breath or not.
```
#Summary
#After doing the analysis of the given data set, I have come across the #fact that this data set lacks information about every age group, it #majorly consists of the people between 55 to 70 year of age, which #makes it difficult to reach at any of the objective that I initially #planned to achieve. But still for this age group I have figured out #that the people who smoke,have shortness of breathness, and coughing #problems, consume alcohol,have higher chances of Lung Cancer, but also #on the other hand there is a significant set of people(although the #percentage is less) who do not smoke, don't have shortness of #breathness and coughing problems and don't consume alcohol also might #get Lung cancer.

#Addition to this I got to know that from the given data set, from #almost every age group, there are more than 50% people who smoke,have #shortness of breathness, and coughing problems, consume alcohol,have #chest pain, anxiety and chronic disease and less than 50% don't, so we #can say that not majority of the people in the given data set are not #living a healthy life style. Also the results obtained reflects that #these are not the only factors which causes lung cancer, beacause there #are people who didnt smoke or have any other issues, but still got lung #cancer. So we can interpret that these are not the only causes of Lung #cancer, they are but not the only ones.

